\pkg{casebase}: An Alternative Framework For Survival Analysis

### 2019-12-05 analysis/paper/paper.tex
add analysis of stanford data

\author{
Sahir Bhatnagar *\\McGill Univeristy \And Maxime Turgeon *\\University of Manitoba \And Jesse Islam\\McGill University \And James Hanley\\McGill Univeristy \And Olli Saarela\\University of Toronto
}
\title{\pkg{casebase}: An Alternative Framework For Survival Analysis}

@@

\Address{
    Sahir Bhatnagar *\\
  McGill Univeristy\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{sahir.bhatnagar@mail.mcgill.ca}\\
  URL: \url{http://sahirbhatnagar.com/}\\~\\
      Maxime Turgeon *\\
  University of Manitoba\\
  318 Machray Hall Winnipeg, MB, Canada R3T 2N2\\
  E-mail: \email{max.turgeon@umanitoba.ca}\\
  URL: \url{http://maxturgeon.ca/}\\~\\
      Jesse Islam\\
  McGill University\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{jesse.islam@mail.mcgill.ca}\\

      James Hanley\\
  McGill Univeristy\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{james.hanley@mcgill.ca}\\
  URL: \url{http://www.medicine.mcgill.ca/epidemiology/hanley/}\\~\\
      Olli Saarela\\
  University of Toronto\\
  Dalla Lana School of Public Health, 155 College Street, 6th floor,
  Toronto, Ontario M5T 3M7, Canada\\
  E-mail: \email{olli.saarela@utoronto.ca}\\
  URL: \url{http://individual.utoronto.ca/osaarela/}\\~\\
  }

@@

\hypertarget{code-formatting}{%
\section*{Code formatting}\label{code-formatting}}
\addcontentsline{toc}{section}{Code formatting}

Don't use markdown, instead use the more precise latex commands:

\begin{itemize}
\item
  \proglang{Java}
\item
  \pkg{plyr}
\item
  \code{print("abc")}
\end{itemize}

@@

The purpose of the \texttt{casebase} package is to provide practitioners
with an easy-to-use software tool to predict the risk (or cumulative
incidence (CI)) of an event, for a particular patient. The following
points should be noted:

@@

As shown by Saarela \& Arjas \citeyearpar{saarela2015non} (and further
expanded in Saarela \citeyearpar{saarela2016case}), writing the
likelihood arising from this data-generating mechanism using the
framework of non-homogenous Poisson processes, we eventually reach an
expression where each person-moment's contribution is of the form
\[\frac{h(t)^{dN(t)}}{\rho(t) + h(t)},\] where \(N(t)\) is the counting
process associated with the event of interest, \(h(t)\) is the
corresponding hazard function, and \(\rho(t)\) is the hazard function
for the Poisson process associated with case-base sampling. This
parametric form suggests that we can readily estimate log-hazards of the
form \(\log(h(t)) = g(t; X)\) using logistic regression, where each
observation corresponds to a person moment, the function \(g(t; X)\) is
linear in a finite number of parameters, and where we treat
\(-\log(\rho(t))\) as an offset.

In Hanley \& Miettinen \citeyearpar{hanley2009fitting}, the authors
suggest performing case-base samping \emph{uniformly}, i.e.~to sample
the base series uniformly from the study base. In terms of Poisson
processes, this sampling strategy corresponds essentially to a
time-homogeneous Poisson process with intensity equal to \(b/B\), where
\(b\) is the number of sampled observations in the base series, and
\(B\) is the total population-time for the study base. More complex
examples are also available; see for example Saarela \& Arjas
\citeyearpar{saarela2015non}, where the probabilities of the sampling
mechanism are proportional to the cardiovascular disease event rate
given by the Framingham score.

@@

@@

This report was generated on 2019-07-25 16:51:47 using the following
computational environment and dependencies:

@@

#> - Session info ----------------------------------------------------------

@@

#>  os       Ubuntu 18.04.2 LTS          

@@

#>  date     2019-07-25                  

@@

#> - Packages --------------------------------------------------------------
#>  package     * version    date       lib source        
#>  assertthat    0.2.1      2019-03-21 [1] CRAN (R 3.6.1)
#>  backports     1.1.4      2019-04-10 [1] CRAN (R 3.6.1)
#>  broom         0.5.2      2019-04-07 [1] CRAN (R 3.6.1)
#>  callr         3.3.1      2019-07-18 [1] CRAN (R 3.6.1)
#>  casebase    * 0.2.1.9000 2019-07-25 [1] local         
#>  cellranger    1.1.0      2016-07-27 [1] CRAN (R 3.6.1)
#>  cli           1.1.0      2019-03-19 [1] CRAN (R 3.6.1)
#>  colorspace    1.4-1      2019-03-18 [1] CRAN (R 3.6.1)
#>  crayon        1.3.4      2017-09-16 [1] CRAN (R 3.6.1)
#>  data.table    1.12.2     2019-04-07 [1] CRAN (R 3.6.1)
#>  desc          1.2.0      2018-05-01 [1] CRAN (R 3.6.1)
#>  devtools      2.1.0      2019-07-06 [1] CRAN (R 3.6.1)
#>  digest        0.6.20     2019-07-04 [1] CRAN (R 3.6.1)
#>  dplyr       * 0.8.3      2019-07-04 [1] CRAN (R 3.6.1)
#>  evaluate      0.14       2019-05-28 [1] CRAN (R 3.6.1)
#>  forcats     * 0.4.0      2019-02-17 [1] CRAN (R 3.6.1)
#>  fs            1.3.1      2019-05-06 [1] CRAN (R 3.6.1)
#>  generics      0.0.2      2018-11-29 [1] CRAN (R 3.6.1)
#>  ggplot2     * 3.2.0      2019-06-16 [1] CRAN (R 3.6.1)
#>  glue          1.3.1      2019-03-12 [1] CRAN (R 3.6.1)
#>  gtable        0.3.0      2019-03-25 [1] CRAN (R 3.6.1)
#>  haven         2.1.1      2019-07-04 [1] CRAN (R 3.6.1)
#>  hms           0.5.0      2019-07-09 [1] CRAN (R 3.6.1)
#>  htmltools     0.3.6      2017-04-28 [1] CRAN (R 3.6.1)
#>  httr          1.4.0      2018-12-11 [1] CRAN (R 3.6.1)
#>  jsonlite      1.6        2018-12-07 [1] CRAN (R 3.6.1)
#>  knitr         1.23       2019-05-18 [1] CRAN (R 3.6.1)
#>  lattice       0.20-38    2018-11-04 [4] CRAN (R 3.5.1)
#>  lazyeval      0.2.2      2019-03-15 [1] CRAN (R 3.6.1)
#>  lubridate     1.7.4      2018-04-11 [1] CRAN (R 3.6.1)
#>  magrittr    * 1.5        2014-11-22 [1] CRAN (R 3.6.1)
#>  Matrix        1.2-17     2019-03-22 [4] CRAN (R 3.5.3)
#>  memoise       1.1.0      2017-04-21 [1] CRAN (R 3.6.1)
#>  mgcv          1.8-28     2019-03-21 [4] CRAN (R 3.5.3)
#>  modelr        0.1.4      2019-02-18 [1] CRAN (R 3.6.1)
#>  munsell       0.5.0      2018-06-12 [1] CRAN (R 3.6.1)
#>  nlme          3.1-140    2019-05-12 [4] CRAN (R 3.6.0)
#>  pillar        1.4.2      2019-06-29 [1] CRAN (R 3.6.1)
#>  pkgbuild      1.0.3      2019-03-20 [1] CRAN (R 3.6.1)
#>  pkgconfig     2.0.2      2018-08-16 [1] CRAN (R 3.6.1)
#>  pkgload       1.0.2      2018-10-29 [1] CRAN (R 3.6.1)
#>  prettyunits   1.0.2      2015-07-13 [1] CRAN (R 3.6.1)
#>  processx      3.4.1      2019-07-18 [1] CRAN (R 3.6.1)
#>  ps            1.3.0      2018-12-21 [1] CRAN (R 3.6.1)
#>  purrr       * 0.3.2      2019-03-15 [1] CRAN (R 3.6.1)
#>  R6            2.4.0      2019-02-14 [1] CRAN (R 3.6.1)
#>  Rcpp          1.0.1      2019-03-17 [1] CRAN (R 3.6.1)
#>  readr       * 1.3.1      2018-12-21 [1] CRAN (R 3.6.1)
#>  readxl        1.3.1      2019-03-13 [1] CRAN (R 3.6.1)
#>  remotes       2.1.0      2019-06-24 [1] CRAN (R 3.6.1)
#>  rlang         0.4.0      2019-06-25 [1] CRAN (R 3.6.1)
#>  rmarkdown     1.14       2019-07-12 [1] CRAN (R 3.6.1)
#>  rprojroot     1.3-2      2018-01-03 [1] CRAN (R 3.6.1)
#>  rstudioapi    0.10       2019-03-19 [1] CRAN (R 3.6.1)
#>  rticles       0.9        2019-07-12 [1] CRAN (R 3.6.1)
#>  rvest         0.3.4      2019-05-15 [1] CRAN (R 3.6.1)
#>  scales        1.0.0      2018-08-09 [1] CRAN (R 3.6.1)
#>  sessioninfo   1.1.1      2018-11-05 [1] CRAN (R 3.6.1)
#>  stringi       1.4.3      2019-03-12 [1] CRAN (R 3.6.1)
#>  stringr     * 1.4.0      2019-02-10 [1] CRAN (R 3.6.1)
#>  survival    * 2.43-3     2018-11-26 [4] CRAN (R 3.5.1)
#>  testthat      2.2.0      2019-07-22 [1] CRAN (R 3.6.1)
#>  tibble      * 2.1.3      2019-06-06 [1] CRAN (R 3.6.1)
#>  tidyr       * 0.8.3      2019-03-01 [1] CRAN (R 3.6.1)
#>  tidyselect    0.2.5      2018-10-11 [1] CRAN (R 3.6.1)
#>  tidyverse   * 1.2.1      2017-11-14 [1] CRAN (R 3.6.1)
#>  usethis       1.5.1      2019-07-04 [1] CRAN (R 3.6.1)
#>  vctrs         0.2.0      2019-07-05 [1] CRAN (R 3.6.1)
#>  VGAM          1.1-1      2019-02-18 [1] CRAN (R 3.6.1)
#>  withr         2.1.2      2018-03-15 [1] CRAN (R 3.6.1)
#>  xfun          0.8        2019-06-25 [1] CRAN (R 3.6.1)
#>  xml2          1.2.0      2018-01-24 [1] CRAN (R 3.6.1)
#>  yaml          2.2.0      2018-07-25 [1] CRAN (R 3.6.1)
#>  zeallot       0.1.0      2018-01-28 [1] CRAN (R 3.6.1)

@@

\begin{CodeOutput}
#> Local:    review-max /home/turgeonm/Documents/git_repos/cbpaper
#> Head:     [c0cb26d] 2019-07-23: Merge pull request #6 from sahirbhatnagar/fixdocker
\end{CodeOutput}
\end{CodeChunk}

>>>>

\author{
Sahir Bhatnagar *\\McGill University \And Maxime Turgeon *\\University of Manitoba \AND Jesse Islam\\McGill University \And James Hanley\\McGill University \And Olli Saarela\\University of Toronto
}
\title{\pkg{casebase}: An Alternative Framework For Survival Analysis}

@@

\Address{
    Sahir Bhatnagar *\\
  McGill University\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{sahir.bhatnagar@mail.mcgill.ca}\\
  URL: \url{http://sahirbhatnagar.com/}\\~\\
      Maxime Turgeon *\\
  University of Manitoba\\
  186 Dysart Road Winnipeg, MB, Canada R3T 2N2\\
  E-mail: \email{max.turgeon@umanitoba.ca}\\
  URL: \url{http://maxturgeon.ca/}\\~\\
      Jesse Islam\\
  McGill University\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{jesse.islam@mail.mcgill.ca}\\

      James Hanley\\
  McGill University\\
  1020 Pine Avenue West Montreal, QC, Canada H3A 1A2\\
  E-mail: \email{james.hanley@mcgill.ca}\\
  URL: \url{http://www.medicine.mcgill.ca/epidemiology/hanley/}\\~\\
      Olli Saarela\\
  University of Toronto\\
  Dalla Lana School of Public Health, 155 College Street, 6th floor,
  Toronto, Ontario M5T 3M7, Canada\\
  E-mail: \email{olli.saarela@utoronto.ca}\\
  URL: \url{http://individual.utoronto.ca/osaarela/}\\~\\
  }

@@

@@

The purpose of the \pkg{casebase} package is to provide practitioners
with an easy-to-use software tool to predict the risk (or cumulative
incidence (CI)) of an event, for a particular patient. The following
points should be noted:

@@

As shown by Saarela \& Arjas \citeyearpar{saarela2015non} (and further
expanded in Saarela \citeyearpar{saarela2016case}), writing the
likelihood arising from this data-generating mechanism using the
framework of non-homogeneous Poisson processes, we eventually reach an
expression where each person-moment's contribution is of the form
\[\frac{h(t)^{dN(t)}}{\rho(t) + h(t)},\] where \(N(t)\) is the counting
process associated with the event of interest, \(h(t)\) is the
corresponding hazard function, and \(\rho(t)\) is the hazard function
for the Poisson process associated with case-base sampling. This
parametric form suggests that we can readily estimate log-hazards of the
form \(\log(h(t)) = g(t; X)\) using logistic regression, where each
observation corresponds to a person moment, the function \(g(t; X)\) is
linear in a finite number of parameters, and where we treat
\(-\log(\rho(t))\) as an offset.

In Hanley \& Miettinen \citeyearpar{hanley2009fitting}, the authors
suggest performing case-base sampling \emph{uniformly}, i.e.~to sample
the base series uniformly from the study base. In terms of Poisson
processes, this sampling strategy corresponds essentially to a
time-homogeneous Poisson process with intensity equal to \(b/B\), where
\(b\) is the number of sampled observations in the base series, and
\(B\) is the total population-time for the study base. More complex
examples are also available; see for example Saarela \& Arjas
\citeyearpar{saarela2015non}, where the probabilities of the sampling
mechanism are proportional to the cardiovascular disease event rate
given by the Framingham score.

@@

\hypertarget{case-study-4stanford-heart-transplant-data}{%
\section{Case study 4--Stanford Heart Transplant
Data}\label{case-study-4stanford-heart-transplant-data}}

Although the previous case studies provide a broad overview of the
capabilities of \pkg{casebase}, they all have two properties in common:

\begin{itemize}
  \item All covariates are fixed, i.e. they do not change over time;
  \item The estimated hazard functions satisfy the "proportional hazard" assumption.
\end{itemize}

The purpose of the next case study is to show how \pkg{casebase} can
also be used for survival analysis problems that do not share these
properties. To this end, we will use the Stanford Heart Transplant Data
\citep[\citet{crowley1977covariance}]{clark1971cardiac}; we will use the
version available in the \pkg{survival} package.

\begin{CodeInput}
R> library(survival)
R> library(casebase)
R> 
R> stanford_popTime <- popTime(jasa, time = "futime", 
R+                             event = "fustat")
R> plot(stanford_popTime)
\end{CodeInput}

\begin{center}\includegraphics{../figures/stanford-poptime-1} \end{center}

Since the exposure is time dependent, we need to manually define the
exposure variable \emph{after} case-base sampling and \emph{before}
fitting the hazard function. For this reason, we will use the
\texttt{sampleCaseBase} function directly.

\begin{CodeInput}
R> library(tidyverse)
R> library(lubridate)
R> 
R> cb_data <- sampleCaseBase(jasa, time = "futime", 
R+                           event = "fustat", ratio = 10)
\end{CodeInput}
\end{CodeChunk}

Next, we will compute the number of days from acceptance into the
program to transplant, and we use this variable to determine whether
each population-moment is exposed or not.

\begin{CodeInput}
R> # Define exposure variable
R> cb_data <- mutate(cb_data,
R+                   txtime = time_length(accept.dt %--% tx.date, 
R+                                        unit = "days"),
R+                   exposure = case_when(
R+                     is.na(txtime) ~ 0L,
R+                     txtime > futime ~ 0L,
R+                     txtime <= futime ~ 1L
R+                   ))
\end{CodeInput}
\end{CodeChunk}

Finally, we can fit the hazard using various linear predictors.

\begin{CodeInput}
R> library(splines)
R> # Fit several models
R> fit1 <- fitSmoothHazard(fustat ~ exposure,
R+                         data = cb_data, time = "futime")
R> fit2 <- fitSmoothHazard(fustat ~ exposure + futime,
R+                         data = cb_data, time = "futime")
R> fit3 <- fitSmoothHazard(fustat ~ exposure + bs(futime),
R+                         data = cb_data, time = "futime")
R> fit4 <- fitSmoothHazard(fustat ~ exposure*bs(futime),
R+                         data = cb_data, time = "futime")
\end{CodeInput}
\end{CodeChunk}

Note that the fourth model (i.e. \texttt{fit4}) includes an interaction
term between exposure and follow-up time. In other words, this model no
longer exhibit proportional hazards. We can then compare the goodness of
fit of these four models using the Akaike Information Criterion (AIC).

\begin{CodeInput}
R> # Compute AIC
R> c("Model1" = AIC(fit1),
R+   "Model2" = AIC(fit2),
R+   "Model3" = AIC(fit3),
R+   "Model4" = AIC(fit4))
\end{CodeInput}

\begin{CodeOutput}
#> Model1 Model2 Model3 Model4 
#>    796    760    730    728
\end{CodeOutput}
\end{CodeChunk}

As we can, the best fit is the fourth model. By visualizing the hazard
functions for both exposed and unexposed individuals, we can more
clearly see how the hazards are no longer proportional.

\begin{CodeInput}
R> # Compute hazards---
R> # First, create a list of time points for both exposure status
R> hazard_data <- expand.grid(exposure = c(0, 1),
R+                            futime = seq(0, 1000,
R+                                         length.out = 100))
R> # Set the offset to zero
R> hazard_data$offset <- 0 
R> # Use predict to get the fitted values, and exponentiate to 
R> # transform to the right scale
R> hazard_data$hazard = exp(predict(fit4, newdata = hazard_data,
R+                                  type = "link"))
R> # Add labels for plots
R> hazard_data$Status = factor(hazard_data$exposure,
R+                             labels = c("NoTrans", "Trans"))
R> 
R> ggplot(hazard_data, aes(futime, hazard, colour = Status)) +
R+     geom_line() +
R+     theme_minimal() +
R+     theme(legend.position = 'top') +
R+     ylab('Hazard') + xlab('Follow-up time')
\end{CodeInput}

\begin{center}\includegraphics{../figures/stanford-hazard-1} \end{center}

The non-proportionality seems to be more pronounced at the beginning of
follow-up than the end. Finally, we can turn these estimate of the
hazard function into estimates of the cumulative incidence functions.

\begin{CodeInput}
R> # Compute absolute risk curves
R> newdata <- data.frame(exposure = c(0, 1))
R> absrisk <- absoluteRisk(fit4, newdata = newdata, 
R+                         time = seq(0, 1000, length.out = 100))
R> 
R> colnames(absrisk) <- c("Time", "NoTrans", "Trans")
R> 
R> # Rearrange the data
R> absrisk <- gather(as.data.frame(absrisk),
R+                   "Status", "Risk", -Time)
R>  
R> ggplot(absrisk, aes(Time, Risk, colour = Status)) +
R+   geom_line() +
R+   theme_minimal() +
R+   theme(legend.position = 'top') +
R+   expand_limits(y = 0.5) +
R+   xlab('Follow-up time') + ylab('Cum. Incidence')
\end{CodeInput}

\begin{center}\includegraphics{../figures/stanford-risk-1} \end{center}

Note that we can easily adapt the code above to the situation where a
patient receives a heart transplant at a point in time of interest, for
example after 30 days.

\begin{CodeInput}
R> # Compute hazards---
R> # First, create a list of time points for both exposure status
R> one_yr_haz <- data.frame(futime = seq(0, 365,
R+                                       length.out = 100))
R> one_yr_haz <- mutate(one_yr_haz,
R+                      offset = 0,
R+                      exposure = if_else(futime < 30, 0, 1))
R> one_yr_haz$hazard = exp(predict(fit4, newdata = one_yr_haz,
R+                                 type = "link"))
R> ggplot(one_yr_haz, aes(futime, hazard)) +
R+   geom_line() +
R+   theme_minimal() +
R+   theme(legend.position = 'top') +
R+   ylab('Hazard') + xlab('Follow-up time') +
R+   geom_vline(xintercept = 30, linetype = 'dashed')
\end{CodeInput}

\begin{center}\includegraphics{../figures/stanford-1y-haz-1} \end{center}

We can then compare the 1-year mortality risk without transplant and
with transplant at 30 days.

\begin{CodeInput}
R> absoluteRisk(fit4, newdata = data.frame(exposure = 0),
R+              time = 365)
\end{CodeInput}

\begin{CodeOutput}
#>         
#> 365 0.27
\end{CodeOutput}

\begin{CodeInput}
R> 
R> # Use the trapezoidal rule to estimate the cumulative hazard
R> min_hazard <- min(one_yr_haz$hazard)
R> max_hazard <- max(one_yr_haz$hazard)
R> increment <- 365/99
R> cumhaz_est <- 0.5*increment*(sum(2*one_yr_haz$hazard) - min_hazard - max_hazard)
R> 1 - exp(-cumhaz_est)
\end{CodeInput}

\begin{CodeOutput}
#> [1] 0.18
\end{CodeOutput}
\end{CodeChunk}

As we can see, the risk estimate at 1-year is about 30\% lower if the
patient receives a heart transplant at 30 days.

@@

This report was generated on 2019-12-05 17:15:04 using the following
computational environment and dependencies:

@@

#> - Session info ---------------------------------------------------------------

@@

#>  os       Ubuntu 18.04.3 LTS          

@@

#>  date     2019-12-05                  

@@

#> - Packages -------------------------------------------------------------------
#>  package     * version    date       lib
#>  assertthat    0.2.1      2019-03-21 [1]
#>  backports     1.1.5      2019-10-02 [1]
#>  broom         0.5.2      2019-04-07 [1]
#>  callr         3.3.2      2019-09-22 [1]
#>  casebase    * 0.2.1.9001 2019-08-13 [1]
#>  cellranger    1.1.0      2016-07-27 [1]
#>  cli           1.1.0      2019-03-19 [1]
#>  colorspace    1.4-1      2019-03-18 [1]
#>  crayon        1.3.4      2017-09-16 [1]
#>  data.table    1.12.6     2019-10-18 [1]
#>  DBI           1.0.0      2018-05-02 [1]
#>  dbplyr        1.4.2      2019-06-17 [1]
#>  desc          1.2.0      2018-05-01 [1]
#>  devtools      2.2.1      2019-09-24 [1]
#>  digest        0.6.23     2019-11-23 [1]
#>  dplyr       * 0.8.3      2019-07-04 [1]
#>  ellipsis      0.3.0      2019-09-20 [1]
#>  evaluate      0.14       2019-05-28 [1]
#>  farver        2.0.1      2019-11-13 [1]
#>  forcats     * 0.4.0      2019-02-17 [1]
#>  fs            1.3.1      2019-05-06 [1]
#>  generics      0.0.2      2018-11-29 [1]
#>  ggplot2     * 3.2.1      2019-08-10 [1]
#>  glue          1.3.1      2019-03-12 [1]
#>  gtable        0.3.0      2019-03-25 [1]
#>  haven         2.2.0      2019-11-08 [1]
#>  hms           0.5.2      2019-10-30 [1]
#>  htmltools     0.4.0      2019-10-04 [1]
#>  httr          1.4.1      2019-08-05 [1]
#>  jsonlite      1.6        2018-12-07 [1]
#>  knitr         1.26       2019-11-12 [1]
#>  labeling      0.3        2014-08-23 [1]
#>  lattice       0.20-38    2018-11-04 [4]
#>  lazyeval      0.2.2      2019-03-15 [1]
#>  lifecycle     0.1.0      2019-08-01 [1]
#>  lubridate   * 1.7.4      2018-04-11 [1]
#>  magrittr    * 1.5        2014-11-22 [1]
#>  Matrix        1.2-17     2019-03-22 [4]
#>  memoise       1.1.0      2017-04-21 [1]
#>  mgcv          1.8-31     2019-11-09 [4]
#>  modelr        0.1.5      2019-08-08 [1]
#>  munsell       0.5.0      2018-06-12 [1]
#>  nlme          3.1-142    2019-11-07 [4]
#>  pillar        1.4.2      2019-06-29 [1]
#>  pkgbuild      1.0.6      2019-10-09 [1]
#>  pkgconfig     2.0.3      2019-09-22 [1]
#>  pkgload       1.0.2      2018-10-29 [1]
#>  prettyunits   1.0.2      2015-07-13 [1]
#>  processx      3.4.1      2019-07-18 [1]
#>  ps            1.3.0      2018-12-21 [1]
#>  purrr       * 0.3.3      2019-10-18 [1]
#>  R6            2.4.1      2019-11-12 [1]
#>  Rcpp          1.0.3      2019-11-08 [1]
#>  readr       * 1.3.1      2018-12-21 [1]
#>  readxl        1.3.1      2019-03-13 [1]
#>  remotes       2.1.0      2019-06-24 [1]
#>  reprex        0.3.0      2019-05-16 [1]
#>  rlang         0.4.2      2019-11-23 [1]
#>  rmarkdown     1.18       2019-11-27 [1]
#>  rprojroot     1.3-2      2018-01-03 [1]
#>  rstudioapi    0.10       2019-03-19 [1]
#>  rticles       0.12       2019-11-12 [1]
#>  rvest         0.3.5      2019-11-08 [1]
#>  scales        1.1.0      2019-11-18 [1]
#>  sessioninfo   1.1.1      2018-11-05 [1]
#>  stringi       1.4.3      2019-03-12 [1]
#>  stringr     * 1.4.0      2019-02-10 [1]
#>  survival    * 2.44-1.1   2019-04-01 [4]
#>  testthat      2.3.1      2019-12-01 [1]
#>  tibble      * 2.1.3      2019-06-06 [1]
#>  tidyr       * 1.0.0      2019-09-11 [1]
#>  tidyselect    0.2.5      2018-10-11 [1]
#>  tidyverse   * 1.3.0      2019-11-21 [1]
#>  usethis       1.5.1      2019-07-04 [1]
#>  vctrs         0.2.0      2019-07-05 [1]
#>  VGAM          1.1-2      2019-11-21 [1]
#>  withr         2.1.2      2018-03-15 [1]
#>  xfun          0.11       2019-11-12 [1]
#>  xml2          1.2.2      2019-08-09 [1]
#>  yaml          2.2.0      2018-07-25 [1]
#>  zeallot       0.1.0      2018-01-28 [1]
#>  source                                  
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  Github (sahirbhatnagar/casebase@aecb816)
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.5.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          
#>  CRAN (R 3.6.1)                          

@@

\begin{CodeOutput}
#> Local:    review-max /home/turgeonm/Documents/git_repos/cbpaper
#> Head:     [77f5e41] 2019-08-02: fix overlapping author names
\end{CodeOutput}
\end{CodeChunk}
